Parallel air palletization and tour planning for simultaneous pickup and delivery

### 2022-11-12 latex/comp_or.tex
All plots working

\usepackage{pgfplots}
\pgfplotsset{compat=newest}
\usepgfplotslibrary{units}
\usepackage{tikz}

@@

@@

%np  time    score

\begin{figure}[h!]
	\begin{center}
		\begin{tikzpicture}[scale=0.8, samples=100]
			\begin{axis}[
				%width=\linewidth, % Scale the plot to \linewidth
				grid=major, 
				grid style={dashed,gray!30},
				xlabel={\bf Scenario 1 computation times (s)},
				ylabel={\bf Scores},
				nodes near coords,
				enlargelimits=0.2,
				legend pos=south east,
				y tick label style={
						/pgf/number format/.cd,
						fixed,
						fixed zerofill,
						precision=3,
						/tikz/.cd,
					},				
				]

				\addplot +[
					only marks,
					point meta=explicit symbolic,
					nodes near coords = {$\pgfmathprintnumber[frac]\np$},
					visualization depends on={\thisrow{np} \as \np},
					font=\small,
				]
				table[x=time, y=score, col sep=comma] {mpShims1.csv};

				\legend{\it parallel processes}
			\end{axis}
		\end{tikzpicture}%
~%
%
		\begin{tikzpicture}[scale=0.8, samples=100]
			\begin{axis}[
				%width=\linewidth, % Scale the plot to \linewidth
				grid=major, 
				grid style={dashed,gray!30},
				xlabel={\bf Scenario 2 computation times (s)},
				ylabel={\bf Scores},
				nodes near coords,
				enlargelimits=0.2,
				legend pos=south east,
				y tick label style={
						/pgf/number format/.cd,
						fixed,
						fixed zerofill,
						precision=3,
						/tikz/.cd,
					}
				]

				\addplot +[
					only marks,
					point meta=explicit symbolic,
					nodes near coords = {$\pgfmathprintnumber[frac]\np$},
					visualization depends on={\thisrow{np} \as \np},
					font=\small,
				]
				table[x=time, y=score, col sep=comma] {mpShims2.csv};

@@

		\caption{{\it mpShims} performance on {\it Scenarios 1 and 2}.}
	\end{center}

\end{figure}\label{fig:mpShims}

Observing Figure \ref{fig:mpShims}, it may be noticed that the best number of processes for {\it Scenario 1} (closest to the upper left corner) is 8. For {\it Scenario 2}, the best number is 16.

>>>>

@@

\usepackage{pgfplots}

\pgfplotsset{
	compat=1.9,
	myplotstyle/.style={
		legend cell align=left,
		every axis plot/.append style={thick},
		legend style={font=\small,draw=none},
		enlargelimits=0.2,
		legend pos=south east,
		y tick label style={ /pgf/number format/.cd, fixed, fixed zerofill, precision=3, /tikz/.cd, },
		grid=major,		
	},
}

@@

\begin{figure}[h!]
	\begin{center}
		\begin{tikzpicture}[scale=0.8, samples=100]
			\begin{axis}[
				myplotstyle,
				xlabel={\bf Scenario 1 computation times (s)},
				ylabel={\bf Scores},
				]
				\addplot+[
				only marks,	
				nodes near coords = {\numProcs{}},
				visualization depends on = {value \thisrow{np} \as \numProcs},						
				]
				table[x=time, y=score, col sep=comma] {mpShims1data20.csv};

				\legend{\it parallel processes}
			\end{axis}
		\end{tikzpicture}%
		~%
		%
		\begin{tikzpicture}[scale=0.8, samples=100]
			\begin{axis}[
				myplotstyle,
				xlabel={\bf Scenario 2 computation times (s)},
				ylabel={\bf Scores},
				]
				\addplot+[
				only marks,	
				nodes near coords = {\numProcs{}},
				visualization depends on = {value \thisrow{np} \as \numProcs},						
				]
				table[x=time, y=score, col sep=comma] {mpShims2data20.csv};

@@

		\caption{ {\it mpShims} performance with $1.2 \times volume$. }
	\end{center}
	\label{fig:mpShimsData20}
\end{figure}

Observing Figure \ref{fig:mpShimsData20}, it may be noticed that the best number of processes for {\it Scenario 1} (closest to the upper left corner) is 8. For {\it Scenario 2}, the best number is 16.

\begin{figure}[h!]
	\begin{center}
		\begin{tikzpicture}[scale=0.8, samples=100]
			\begin{axis}[
				myplotstyle,
				xlabel={\bf Scenario 1 computation times (s)},
				ylabel={\bf Scores},
				]
				\addplot+[
				only marks,	
				nodes near coords = {\numProcs{}},
				visualization depends on = {value \thisrow{np} \as \numProcs},						
				]
				table[x=time, y=score, col sep=comma] {mpShims1data50.csv};

				\legend{\it parallel processes}
			\end{axis}
		\end{tikzpicture}%
		~%
		%
		\begin{tikzpicture}[scale=0.8, samples=100]
			\begin{axis}[
				myplotstyle,
				xlabel={\bf Scenario 2 computation times (s)},
				ylabel={\bf Scores},
				]
				\addplot+[
				only marks,	
				nodes near coords = {\numProcs{}},
				visualization depends on = {value \thisrow{np} \as \numProcs},						
				]
				table[x=time, y=score, col sep=comma] {mpShims2data50.csv};

		\caption{{\it mpShims} performance with $1.5 \times volume$.}
	\end{center}
	\label{fig:mpShimsData50}
\end{figure}

Observing Figure \ref{fig:mpShimsData50}, it may be noticed that the best number of processes for {\it Scenario 1} (closest to the upper left corner) is 8. For {\it Scenario 2}, the best number is 16.

\begin{figure}[h!]

	\begin{center}
		\begin{tikzpicture}[scale=0.8, samples=100]
			\begin{axis}[
				myplotstyle,
				xlabel={\bf Scenario 1 computation times (s)},
				ylabel={\bf Scores},
				]
				\addplot+[
				only marks,	
				nodes near coords = {\numProcs{}},
				visualization depends on = {value \thisrow{np} \as \numProcs},						
				]
				table[x=time, y=score, col sep=comma] {Shims_p1data100.csv};

				\legend{\it parallel processes}
			\end{axis}
		\end{tikzpicture}%
		~%
		%
		\begin{tikzpicture}[scale=0.8, samples=100]
			\begin{axis}[
				myplotstyle,
				xlabel={\bf Scenario 2 computation times (s)},
				ylabel={\bf Scores},
				]
				\addplot+[
				only marks,	
				nodes near coords = {\numProcs{}},
				visualization depends on = {value \thisrow{np} \as \numProcs},						
				]
				table[x=time, y=score, col sep=comma] {Shims_p2data100.csv};

		\caption{{\it mpShims} performance with $2.0 \times volume$.}
	\end{center}
	\label{fig:mpShimsData100}
\end{figure}

Observing Figure \ref{fig:mpShimsData100}, it may be noticed that the best number of processes for {\it Scenario 1} (closest to the upper left corner) is 8. For {\it Scenario 2}, the best number is 16.
